Comprehensive Comparison of Deep Learning Models for Lung and COVID-19 Lesion Segmentation in CT scans

### 2020-09-16 ms.tex
fix Makefile {make test}

\begin{abstract}
	Recently there has been an explosion in the use of Deep Learning (DL) methods for medical image segmentation.
	However the field's reliability is hindered by the lack of a common base of reference for accuracy/performance evaluation and the fact that previous research uses different datasets for evaluation.
	In this paper, an extensive comparison of DL models for lung and COVID-19 lesion segmentation in Computerized Tomography (CT) scans is presented, which can also be used as a benchmark for testing medical image segmentation models.
	Four DL architectures (Unet, Linknet, FPN, PSPNet) are combined with $25$ randomly initialized and pretrained encoders (variations of VGG, DenseNet, ResNet, ResNext, DPN, MobileNet, Xception, Inception-v4, EfficientNet), to construct $200$ tested models.
	Three experimental setups are conducted for lung segmentation, lesion segmentation and lesion segmentation using the original lung masks.
	A public COVID-19 dataset with $100$ CT scan images ($80$ for train, $20$ for validation) is used for training/validation and a different public dataset consisting of $\DTLfetch{keys_values}{key}{num_slices_test}{value}$ images from $9$ CT scan volumes for testing.
	Multiple findings are provided including the best architecture-encoder models for each experiment as well as mean Dice results for each experiment, architecture and encoder independently.
	Finally, the upper bounds improvements when using lung masks as a preprocessing step or when using pretrained models are quantified.
	The source code and $600$ pretrained models for the three experiments are provided, suitable for fine-tuning in experimental setups without GPU capabilities.
\end{abstract}

>>>>

\begin{abstract}
	Deep Learning (DL) methods are extensively used for medical image segmentation.
	However the field's reliability is hindered by the lack of a common base of reference for accuracy/performance evaluation and that previous research uses different datasets for evaluation.
	In this paper, an extensive comparison of DL models for lung and COVID-19 lesion segmentation in Computerized Tomography (CT) scans is presented, which can also be used as a benchmark for testing medical image segmentation models.
	Four DL architectures (Unet, Linknet, FPN, PSPNet) are combined with $25$ randomly initialized and pretrained encoders (variations of VGG, DenseNet, ResNet, ResNext, DPN, MobileNet, Xception, Inception-v4, EfficientNet), to construct $200$ tested models.
	Three experimental setups are conducted for lung segmentation, lesion segmentation and lesion segmentation using the original lung masks.
	A COVID-19 dataset with $100$ CT scan images is used for training/validation and a different dataset consisting of $\DTLfetch{keys_values}{key}{num_slices_test}{value}$ images from $9$ CT scan volumes for testing.
	Multiple findings are provided including the best architecture-encoder models for each experiment as well as mean Dice results for each experiment, architecture and encoder independently.
	The source code and $600$ pretrained models for the three experiments are provided, suitable for fine-tuning in experimental setups without GPU capabilities.
\end{abstract}
